### 2022-05-30 manuscript/hiv-gwas.tex
Update on Overleaf.

>>>>

\begin{figure}[H]
	\begin{center}
		\includegraphics[width=0.7\linewidth]{figures/example_simulation_trait_values}
		\caption{Example simulated data from two evolutionary scenarios where (left) a phylogenetic correction does not improve GWAS power and (right) where it does. Both data sets were simulated with selection strength = 0.1 time $^{-1}$ and all other parameters fixed as in the full simulation study.}
		\label{fig:simulationTraitExample}
	\end{center}
\end{figure}
